**Density Dependence**

### 2022-12-28 Rmd/runDD.Rmd
with mat

>>>>

Mass-at-age is assumed to vary with total biomass, we assume that estimates of mass-at-age ({W_t}^\prime) are based on observations around $B_{MSY}$ and if total biomass increased density dependence results in a decline in the expected value of $W_a$, i.e. $W_t = {W_t}^\prime a(B_t/B_{MSY})^b$

Maturity at age is modelled by a logistic relationship $f(x) = \frac{1}{1+e^{-r(W-$W_50$)}}$ where $W_{50}$ is the weight when $50%$ are mature, and $r$ a parameter that determines how fast individuals mature.
